---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  fig.path = "man/figures/README-", # Organizes images into a specific folder
  dpi = 300                         # Ensures crisp images on GitHub
)
```

# F1 Stories: Data-Driven Narratives

<!-- badges: start -->
<!-- badges: end -->

This project is a deep dive into Formula 1 telemetry and results, with a specific focus on the 2026 Technical Revolution. While many look at the standings, "F1 Stories" looks at the "why."

## Key Research Questions:

* The Hybrid Shift: How does the 50/50 ICE-to-Electric power split change driver throttle application?

* The Aero Game: Visualizing the impact of active aerodynamics on straight-line speed.

* The Teammate Duel: Who is winning the internal battle when the car is a "black box" of new regulations?

## 2025 Performance Baseline
Before diving into the 2026 data, we establish a baseline using the final standings of the 2025 season.

```{r baseline_plot, echo = FALSE, message = FALSE, warning = FALSE, dpi = 300}
source("scripts/01_baseline_2025.R")
constructor_points
```
